The title

### 2023-01-17 docs/draft/draft.Rmd
formatting changes
stopped at line 103

The development of online education has been evolving over the past few decades, offering an alternative to deliver learning in a more convenient manner to individuals who could not be physically present in the traditional educational classroom.  Of special interest is the research and development of language education across time and how online education has played a role in this development, as well as the implementation of communicative strategies within it. Research and technological advances allowed online language education to develop greatly, however, the Covid-19 pandemic appeared to be its hardest challenge to date. According to the National Center for Education Statistics (2022), during the fall of 2020 over 75 percent of undergraduate students (11.8 million) were enrolled in at least one online course, whereas 44 percent (7.0 million) of all undergraduate students exclusively enrolled in online courses. Compared to fall 2019, these numbers represent a 97 percent increase in undergraduates taking at least one online course (11.8 million vs. 6.0 million) and a 186 percent increase in undergraduate students enrolled exclusively in online courses (7.0 million vs. 2.4 million).

Online learning comes with a new set of challenges that are not found in a traditional classroom setting, especially when, for many, it was not an option to have class anywhere but virtually. Being forced to switch modalities had consequences, both from the teachers’ and students’ perspectives, as they were either not ready for the change or lacked many materials. Top Hat (2020) did a major survey on undergraduate students’ and teachers’ perceptions during the online emergency switch in US universities. Their findings within students taking a language class were that overall, the quality of instruction received was worse in comparison to the in-person learning setting. In the same way, a vast majority of students felt that the class experience was unengaging as they missed spending time with faculty and fellow students. Within this swift change to online settings, many students also found that their academic load was not only reduced but also experienced problems with using online tools.

Language attitudes are key in the language learning environment, as they can determine the success of a student [ eg @thompson2021attitudes]. A learner with a positive attitude toward a learning environment will more likely succeed than a learner who finds the environment difficult or disengaged. Specifically, the attitudes in online learning have been shown to play a key role as students are physically detached from the learning environment, and rely more on self-regulation abilities [ @alqurashi2016self; @horvat2015student; @ke2013constructs; @lan2010using]. Within this framework, anxiety has been linked in several research studies [e.g.,@teimouri2019second] as an indicator of poor linguistic development. Interestingly, anxiety and the fear of the unknown is a feeling that fluctuates with empirical contact throughout the academic appointment. Furthermore, @webb2014flipping studied the attitudes of students and teachers in a flipped online classroom of Chinese. Their results showed an incremental fluctuation in their perception. That is, they found distance education would not meet student expectations at first, but through the semester they found a growing acceptance that led to successful results by the end of a 15-week term. A similar psychological development is observed in @ushida2005role study which investigated the changes in students’ attitudes and motivation over time in online language courses. Their results showed a similar evolution within the student’s attitudes, as students reduced their anxiety level as the semester progressed, feeling more comfortable with the system as well as the teaching materials by the end of the educational term. 
Past educational experiences and abilities acquired through these experiences have an effect on how students shape attitudes toward a new learning encounter (Saito et al. 2018), as well as the familiarity and complexity of the instruments that the course requires (@heckel2019pride), which might involve some training and assistance before the beginning of the online course. During the covid outbreak, students and educators lacked experience with online tools as well as time to prepare, @tomasik2021educational, leading to an overall feeling of less effective education Top hat (2020), @hodges2020difference, @lee2022factors. While the immediate transition to online education seemed rushed in @ruiz2022transitioning the stress levels of undergraduates diminished from the beginning to the end of the academic term as they became more familiar with the instructional materials, and therefore gained more experience with their newfound educational setting. Their study of US undergraduates found varied responses in which some students enjoyed the increased autonomy and self-paced learning opportunities offered by the new online format. Along the same line, a survey of university students found a common belief that online education helped them continue their education while still learning, observing, and improving the quality of teaching as their professors gained more experience with the teaching instruments [@chakraborty2021opinion]. 
The outbreak of COVID-19 has caused online teaching and learning to evolve very rapidly during the past two years. This was a global phenomenon in the history of language education which had many educational consequences that students most likely will continue to experience when approaching online education. With a global decrease in Covid-19 cases, most US universities slowly began to switch to a pre-pandemic educational setting or blend hybrid classes. The goal of this paper is dual, first to determine if online education is still in demand among our undergraduate students, and to identify what are the attitudes towards it in a context where online education is no longer mandatory. Our second goal is to better understand how our new post-pandemic reality modulates tendencies in university language class enrollment.

>>>>

The development of online education has been evolving over the past few decades, offering an alternative to delivering learning in a more convenient manner to individuals who could not be physically present in the traditional educational classroom.  
<!--- we might consider (not rn but to be discussed) deleted the "could not be physically present" part, it could open a can of worms---> 
Of special interest is the research and development of language education across time and how online education has played a role in this development, as well as the implementation of communicative strategies within it. 
<!--- I think the above sentence might be unnecessary bc we don't necessarily talk about communicative strategies --> 
Research and technological advances allowed online language education to develop greatly, <!--- for example, x, y, z helps students to do a, b, and c. then start with the next sentence--->  
However, the Covid-19 pandemic appeared to be its hardest challenge to date. <!--- in what way? are we saying covid was a challenge for online learning? this seems to go against the previous sentences saying that techology had advanced and online learning has developed-->
According to the National Center for Education Statistics (2022), during the fall of 2020 over 75 percent of undergraduate students (11.8 million) were enrolled in at least one online course, whereas 44 percent (7.0 million) of all undergraduate students exclusively enrolled in online courses (*insert citation*). 
Compared to Fall 2019, these numbers represent a 97 percent increase in undergraduates taking at least one online course (11.8 million vs. 6.0 million) and a 186 percent increase in undergraduate students enrolled exclusively in online courses (7.0 million vs. 2.4 million).

Online learning comes with a new set of challenges that are not found in a traditional classroom setting, especially when, for many, it was not an option to have class anywhere but virtually. 
Being forced to switch modalities had consequences, both from the teachers’ and students’ perspectives, as they were either not ready for the change or lacked many materials. 
Top Hat (2020) did a major survey on undergraduate students’ and teachers’ perceptions during the online emergency switch in US universities. 
Their findings within students taking a language class were that overall, the quality of instruction received was worse in comparison to the in-person learning setting (*insert citation*)
In the same way, a vast majority of students felt that the class experience was unengaging as they missed spending time with faculty and fellow students. 
Within this swift change to online settings, many students also found that their academic load was not only reduced but also experienced problems with using online tools. <!--- i'm going to think about how to reframe this paragraph --->

Language attitudes are key in the language learning environment, as they can determine the success of a student [ eg @thompson2021attitudes]. 
A learner with a positive attitude toward a learning environment will more likely succeed than a learner who finds the environment difficult or disengaged.
Specifically, the attitudes in online learning have been shown to play a key role as students are physically detached from the learning environment, and rely more on self-regulation abilities [ @alqurashi2016self; @horvat2015student; @ke2013constructs; @lan2010using]. 
Within this framework, anxiety has been linked in several research studies [e.g.,@teimouri2019second] as an indicator of poor linguistic development. 
Interestingly, anxiety and the fear of the unknown is a feeling that fluctuates with empirical contact throughout the academic appointment. 
Furthermore, @webb2014flipping studied the attitudes of students and teachers in a flipped online classroom of Chinese. 
Their results showed an incremental fluctuation in their perception. 
That is, they found distance education would not meet student expectations at first, but through the semester they found a growing acceptance that led to successful results by the end of a 15-week term. 
A similar psychological development is observed in @ushida2005role study which investigated the changes in students’ attitudes and motivation over time in online language courses. 
Their results showed a similar evolution within the student’s attitudes, as students reduced their anxiety level as the semester progressed, feeling more comfortable with the system as well as the teaching materials by the end of the educational term. 
Past educational experiences and abilities acquired through these experiences have an effect on how students shape attitudes toward a new learning encounter (Saito et al. 2018), as well as the familiarity and complexity of the instruments that the course requires (@heckel2019pride), which might involve some training and assistance before the beginning of the online course. 
During the covid outbreak, students and educators lacked experience with online tools as well as time to prepare, @tomasik2021educational, leading to an overall feeling of less effective education Top hat (2020), @hodges2020difference, @lee2022factors. 
While the immediate transition to online education seemed rushed in @ruiz2022transitioning the stress levels of undergraduates diminished from the beginning to the end of the academic term as they became more familiar with the instructional materials, and therefore gained more experience with their newfound educational setting. 
Their study of US undergraduates found varied responses in which some students enjoyed the increased autonomy and self-paced learning opportunities offered by the new online format. 
Along the same line, a survey of university students found a common belief that online education helped them continue their education while still learning, observing, and improving the quality of teaching as their professors gained more experience with the teaching instruments [@chakraborty2021opinion].

The outbreak of COVID-19 has caused online teaching and learning to evolve very rapidly during the past two years. 
This was a global phenomenon in the history of language education which had many educational consequences that students most likely will continue to experience when approaching online education. 
With a global decrease in Covid-19 cases, most US universities slowly began to switch to a pre-pandemic educational setting or blend hybrid classes. 
The goal of this paper is dual, first to determine if online education is still in demand among our undergraduate students, and to identify what are the attitudes towards it in a context where online education is no longer mandatory. Our second goal is to better understand how our new post-pandemic reality modulates tendencies in university language class enrollment.
